Spatial Reasoning and Statistical Graphics

### 2014-10-30 Paper/Draft1/TestingVisualAptitude.Rnw
Wording change...
Comment addition

Participants will complete the following tasks (sample pictures included, full stimuli set will be added to the appendix once we are sure there is no need for follow-up experiments). Tasks are designed so that participants are under time pressure; they are not expected to complete all of the problems in each section. This provides more discrimination between high scorers and prevents score compression at the top of the range.

@@

In addition to these tests, participants were asked to complete a questionnaire which includes questions about colorblindness, mathematical background, self-perceived verbal/mathematical/artistic skills, time spent playing video games, and undergraduate major. \comment{XXX should we classify majors into STEM/non-STEM? - there's a ton of literature and interest that we could potentially tap into} These questions are designed to assess different factors which may influence a participant's skill at reading graphs and performing spatial tasks.

>>>>

Participants will complete several cognitive tests designed to measure spatial and reasoning ability. Tasks are designed so that participants are under time pressure; they are not expected to complete all of the problems in each section. This provides more discrimination between high scorers and prevents score compression at the top of the range.

@@

In addition to these tests, participants were asked to complete a questionnaire which includes questions about colorblindness, mathematical background, self-perceived verbal/mathematical/artistic skills, time spent playing video games, and undergraduate major. \comment{XXX should we classify majors into STEM/non-STEM? - there's a ton of literature and interest that we could potentially tap into \\\textit{I'm not opposed, but we have to decide where ag-majors fall... not everything is easily classifiable. Psychology is another problem: I was very STEM-psychology, but you don't have to be.}} These questions are designed to assess different factors which may influence a participant's skill at reading graphs and performing spatial tasks.
